\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-01-30 paper.tex
rewrite MCMC

\subsection{MCMC}
\label{subsec:mcmc}
Markov Chain Monte Carlo (MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution $ \pi (x) $.
A set of samples are generated to approximate the desired distribution $ \pi (x) $.
Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important areas, which usually brings better efficiency.
Hamiltonian Monte Carlo(HMC)~\cite{N11} is introduced to provide better efficiency in converging to a desired distribution.
It adopts physical system dynamics to propose future states in the Markov chain.
The concept origins from Hamiltonian dynamics, which models the movement of an object.
Given the position $ x $ and the momentum $ q $ of an object, the system energy can be written as $ H(x,q) = U(x) + K(q) $, in which $ U(x) $ is the potential energy and $ K(q) $ is the kinetic energy.
The movement of the object (how $ x $ and $ q $ change over time) is determined by
$ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.
By the association between energy and a canonical distribution, a joint distribution for the states $ x $ and $ q $ can be created from a Hamiltonian dynamics, which is 
$ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) = \frac{1}{Z} \exp ( -U(x) / T) \exp (-K(q) / T) $.
If we define $ U(x) = - \log ( \pi(x) T ) $, $ P(x, q) $ can be rewritten as $ P(x, q) = \pi (x) \frac{1}{Z} \exp (-K(q) / T) $.
Because the state $ x $ and the the momentum  $ q $ are independent, we can sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ (as an auxiliary variable).
The collected set of $ x $ is equivalent to sampling from $ \pi(x) $.
We are going to integrate this idea into our sampling framework of efficiently generating samples under kinetic constraints.

>>>>

\subsection{MCMC}
\label{subsec:mcmc}
Markov Chain Monte Carlo (MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution $ \pi (x) $.
A set of samples are generated to approximate the desired distribution $ \pi (x) $.
Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important areas, which usually brings better efficiency.
Hamiltonian Monte Carlo(HMC)~\cite{N11} is introduced to provide better efficiency in converging to a desired distribution.
It adopts physical system dynamics to propose future states in the Markov chain.
The concept origins from Hamiltonian dynamics, which models the movement of an object, the position $ x $ and the momentum $ q $ over time $ t $.
Define a system energy $ H $ of an object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ H(x,q) = U(x) + K(q) $.
The kinetic energy $ K(q) $ is determined by the momentum $ q $ of the object, while the potential energy $ U(x) $ is determined by the position $ x $ of the object.
By the Hamiltonian equation, the movement of the object can be predicted by
$ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.
This provides an approach of the gradient descent by following the decrease of an associated potential energy.
Thus, HMC simulates the Hamiltonian dynamics that moves samples towards a target distribution while avoiding random walks.

A canonical distribution bridges an energy with a probability distribution.
If two different states have the same energy, the probabilities of them are equivalent.
A set of samples from such a distribution can be equivalent to a set of samples driven by an associated energy.
By using the system energy $ H(x, q) $, we can defines a canonical distribution $ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) $.
Because $ H(x,q) = U(x) + K(q) $, $ P(x, q) $ can be factorized into two independent terms, which is written as $ P(x, q) = \frac{1}{Z} \exp ( -U(x) / T) \exp (-K(q) / T) $.
The independence implies that we can sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ (as an auxiliary variable) in order to sample from a canonical distribution $ \propto \exp ( -U(x) / T) $.
If we have a target distribution $ \pi(x) $ of state $ x $ and define a potential energy in the form $  U(x) = - \log ( \pi(x) T ) $, we can have the canonical distribution equal to $ \pi(x) $.
The collected set of $ x $ is equivalent to sampling from $ \pi(x) $.
Thus, we can use simulating the Hamiltonian dynamics to generate a set of samples from a target distribution $ \pi (x) $.

We are going to integrate this idea into our sampling framework of efficiently generating samples under kinetic constraints. 
We define a target distribution as a uniform distribution subject to kinetic constraints and cost budgets.
